Incentivizing Exploration with Unbiased History

### 2018-10-28 3level.tex
comments for 3level

\section{Adaptive Policy with Three Levels}
\label{sec:3level}
\swcomment{rewrote below}
Now we demonstrate how to design a 3-level policy to incentivize
adaptive exploration and improve the $O(T^{2/3})$ regret rate to
$\tilde O(T^{4/7})$. In \Cref{sec:llevel}, we will show how to extend
this idea to achieve a regret rate of $\tilde O(T^{1/2})$. For
simplicity, we will focus on the setting with 2 arms\niedit{, although our results can be extended to a constant number of arms $K$}. \nicomment{I think that's true, but if not, then we're not focusing on 2 arms for ``simplicity''.}

The policy consists of three phases, each of which corresponds to a
level (see Figure~\ref{fig:3level}).  In the first level, the policy
performs the first round of exploration over the first
$(S\cdot T_1\cdot T_G)$ agents, where $T_1 = T^{4/7}\log^{-1/7}(T)$
and $S = 2^{10}\log(T)$. In particular, the policy randomly partitions
the agents into $S$ groups such that each group consists of $T_1$ runs
of \ALGG with $T_G$ rounds. In the second level, the policy performs
further exploration on the next $(S\cdot T_2)$ agents by incorporating
data collected in the first level, where
$T_2 = T^{6/7}\log^{-5/7}(T)$. The agents are again partitioned into
$S$ groups such that the agents in the $s$-th group are shown the same
sub-history from the $s$-th group in the first level. In the third
level, the policy exploits by showing all remaining agents the entire
history from the first two levels. \nicomment{This comment applies to the 2level too; why not allow the guys within the last level see each other?  Seems like this would still work but be more of a headache to prove -- would have to argue the empirical means can't move around too much in the sub-terminal levels, but it makes a big qualitative difference because now everyone sees a vanishingly small fraction of the history whereas with this modification a fraction approaching 1 of the people see a fraction approaching 1 of the history.}

>>>>

\section{Adaptive Policy with Three Levels}
\label{sec:3level}
\swcomment{rewrote below}
Now we demonstrate how to design a 3-level policy to incentivize
adaptive exploration and improve the $O(T^{2/3})$ regret rate to
$\tilde O(T^{4/7})$. In \Cref{sec:llevel}, we will show how to extend
this idea to achieve a regret rate of $\tilde O(T^{1/2})$. For
simplicity, we will focus on the setting with 2 arms\niedit{, although our results can be extended to a constant number of arms $K$}. \nicomment{I think that's true, but if not, then we're not focusing on 2 arms for ``simplicity''.} \jmcomment{It is true. We only show this extension for $l$-level tho.}

The policy consists of three phases, each of which corresponds to a
level (see Figure~\ref{fig:3level}).  In the first level, the policy
performs the first round of exploration over the first
$(S\cdot T_1\cdot T_G)$ agents, where $T_1 = T^{4/7}\log^{-1/7}(T)$
and $S = 2^{10}\log(T)$. In particular, the policy randomly partitions
the agents into $S$ groups such that each group consists of $T_1$ runs
of \ALGG with $T_G$ rounds. In the second level, the policy performs
further exploration on the next $(S\cdot T_2)$ agents by incorporating
data collected in the first level, where
$T_2 = T^{6/7}\log^{-5/7}(T)$. The agents are again partitioned into
$S$ groups such that the agents in the $s$-th group are shown the same
sub-history from the $s$-th group in the first level. In the third
level, the policy exploits by showing all remaining agents the entire
history from the first two levels. \nicomment{This comment applies to the 2level too; why not allow the guys within the last level see each other?  Seems like this would still work but be more of a headache to prove -- would have to argue the empirical means can't move around too much in the sub-terminal levels, but it makes a big qualitative difference because now everyone sees a vanishingly small fraction of the history whereas with this modification a fraction approaching 1 of the people see a fraction approaching 1 of the history.} \jmcomment{To do it for the last level is actually easy. It would be headache to do it for the second level as we want to prove anti-concentration in the second level. On the other hand, we have the property that agents see $1/polylog$ fraction of history in our final result for $l$-level. A different point of view is that, seeing each other requires more interaction, our policy has the nice property that the interaction is very minimal except the initial greedy runs.}

### 2018-10-28 llevel-overview.tex
comments for 3level

In Theorem \ref{thm:llevel-2}, we show a recommendation policy with instance-dependent regret guarantee. This policy has the same structure as the one in Theorem \ref{thm:llevel-1} but different parameters. Its expected regret depends on $\Delta$ which is the difference between the largest mean and second largest mean of arms. Its regret bound outperforms the one in Theorem \ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$. The only downside is that this policy requires more levels, i.e. $O(\log(T)/\log\log(T))$ levels. It also has the property that each agent observes a good fraction of history before its round.

>>>>

In Theorem \ref{thm:llevel-2}, we show a recommendation policy with instance-dependent regret guarantee. This policy has the same structure as the one in Theorem \ref{thm:llevel-1} but different parameters. Its expected regret depends on $\Delta$ which is the difference between the largest mean and second largest mean of arms and its construction does not depend on $\Delta$. Its regret bound outperforms the one in Theorem \ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$. The only downside is that this policy requires more levels, i.e. $O(\log(T)/\log\log(T))$ levels. It also has the property that each agent observes a good fraction of history till its round.
